\cvsection{Presentations and Media Appearances}
\begin{cventries}
      \cventry
    {`Engineering Models for Inertially-Fixed Forces on Hingeless Rigid Rotors in Non-Uniform Inflow'} % Short desc
    {Presenter} % Place
    {\hspace{-2cm}American Helicopter Society 74, Phoenix AZ} % Where
    {May 2018}{} % Date
%    {Presentation of a novel harmonic wake model for a propeller at incidence that I developed (journal paper being written).}
%    \vspace{.5cm}
    \cventry
    {`The challenges of commercial wind tunnel testing in a modern age'} % Short desc
    {Plenary speaker} % Place
    {\hspace{-2cm}Airbus DiPaRT Conference, Bristol} % Where
    {April 2016}{} % Date
    
    \cventry
    {`Reduced order modelling of rotary aerodynamics', `Commercial WT Testing'} % Short desc
    {Invited Lecturer} % Place
    {\hspace{-6cm}University of Glasgow, University of Bristol, Loughborough University } % Where
    {Numerous 2015-2018}{} % Date
    \cventry{SME - `Rotorcraft Safety' after the Clutha Helicopter Crash}{BBC Evening News}{2013}{}{}
   
   
\end{cventries}

%\cvsection{Classes Taught}
%
%\begin{cvskills}
%\vspace{.2cm}
%\cvskill{}{\hspace{-4.5cm}\bodyfont Full courses delivered at IIT:}
%\vspace{.2cm}
%\cvskill{Aircraft Flight Mechanics}{Fourth-year class comprising \textsl{aircraft performance}, \textsl{development of a/c equations of motion}, \textsl{linearisation and presentation in concise form}, \textsl{flight dynamics}, and \textsl{feedback control}}
%\vspace{.2cm}
%\cvskill{Aerospace Laboratory I}{Third year class covering \textsl{analogue electronics}, \textsl{data acquisition}, \textsl{data reduction}, \textsl{wind tunnel experimentation}}
%\vspace{.2cm}
%\cvskill{Intro. to the Profession}{First-year class covering \textsl{basic aircraft anatomy}, \textsl{aeronautical nomenclature}, \textsl{engineering communication},\newline \textsl{engineering ethics}, \textsl{Python for aerospace engineers}, and \textsl{an introduction to the circulatory theory of lift}}
%\vspace{.2cm}
%\cvskill{Mechanics of Aerostructures}{Third year class introducing \textsl{principle of virtual displacements}, \textsl{the fundamentals of finite-element methods \newline (setting up a $[K]\vec{Q}=\vec{P}$ problem)}, and \textsl{static aeroelastic phenomena (divergence and control reversal)}}
%\vspace{.2cm}
%\cvskill{Rotary Aerodynamics}{A summer course comprising \textsl{blade element theory}, \textsl{general momentum theory}, and \textsl{vortex methods}}\\
%
%\vspace{.2cm}
%\cvskill{}{\hspace{-4.5cm}\bodyfont Previous partial experience in teaching during PhD:}
%
%\vspace{.2cm}
%\cvskill{Aeroelasticity}{UG and Masters level courses solving static and dynamic aeroelastic phenomena - have full course materials\newline and permission to continue course from PhD advisor}
%\cvskill{Aircraft Propulsion}{Taught the propeller half of UoG course during PhD - have course materials for turbomachinery section}
%
%
%\end{cvskills}
%
%\cvsection{Research Interests}
%
%\begin{cvskills}
%
%\cvskill{Propellers}{Swept blade effects, aeroelasticity, off-design loading}
%\cvskill{Flight Dynamics}{Determination of stability derivatives from flight test data, effects of propeller harmonic loading thereupon}
%\cvskill{Machine Learning}{Automatic calibration via recognition of analogue transducer dials}
%\cvskill{Education}{Introduction of Python-based chatbot quizzes in Slack, to gauge student topic understanding}
%
%
%\end{cvskills}

\cvsection{Awards and Competitions}
\vspace{.1cm}
\begin{cventries}
      \cventry
    {Full detail at \textbf{\href{https://www.iit.edu/news/engineering-faculty-member-awarded-provosts-inaugural-online-teaching-award?fbclid=IwAR1rnJJH0X0j_ZoT1OAlPZm4HNpREQp_A0Hx-8LIhM_4BP7b8K9ChcNPFFI}{bit.ly/3nppfeA}}} % Short desc
    {Provost's Inaugural Online Teaching Award} % Place
    {Illinois Institute of Technology} % Where
    {Dec 2020}{The award identifies faculty who have adapted to the circumstances of the past year due to the coronavirus pandemic, most courses have followed an online or hybrid model-and created exceptional online learning experiences in the fall 2020 semester.}
%    \vspace{.5cm}
    \cventry
    {Inter-University Competition in Science Communication} % Short desc
    {Science Slam - Winner} % Place
    {Cambridge University} % Where
    {2013}{A competition to communication PhD theses to the general public, in a pub. Won joint first place in a set of five entrants.}
   
\end{cventries}

\cvsection{Publications}

{\small Majority of career and doctoral research has been spent on commercially-sensitive and/or classified projects - limited publications:}\vspace{.25cm}

\begin{cvitems}
	\item Smith, H. R. (2018). \textsl{Engineering models for inertially-fixed forces caused by hingeless rigid rotors in non-uniform inflow: a problem for compound helicopters.} in VFS Forum 74 Conference Proceedings; Phoenix; Vertical Flight Society. 
	\item Smith, H. R. (2015). \textsl{Engineering models of aircraft propellers at incidence} (Doctoral dissertation, University of Glasgow).	
\end{cvitems}

